Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-15 WSSSPE4_report/WSSSPE4_report.tex
more accurate description of projects process
added description of NLeSC lightning talk

    \item \textbf{Willem Robert van Hage\textsuperscript{\textasteriskcentered},
    Jason Maassen and Rob van Nieuwpoort: \textit{Software Impact Measurement at the
    Netherlands eScience Center}}~\cite{vanHage:2016ws}.
    \note{Description}

@@

Once we had the walls covered in ideas, we had people organically form groups around the flip charts on the wall\footnote{Photos of the flipcharts: \url{https://github.com/WSSSPE/media/tree/master/WSSSPE4-photos}}. We asked them to work in Google Docs, \todo{find and cite these docs?  Is this really true, or was this all done in flip charts?} using a template for Vision, Gaps, and Projects.  For those folk who worked on Vision and Gaps, after an hour, we encouraged them to finish their Vision or Gap Google Doc, and to find and join or start working on a project with a group. This led to the 12 groups that are discussed in the rest of this section, specifically:
\begin{enumerate}
\item Verifying best practices \& metrics for sustainable research software
\item Software Sustainability Alliance
\item Scientific Software Prototyping Infrastructure (S2PI)
\item Standard metadata for software (CodeMeta)
\item White paper on developing sustainable softwarez
\item Social science for scientific software
\item Software best practices for undergraduates
\item Meaningful metrics for sustainable software
\item Coordinating access to CI for research software
\item Software engineering processes tailored for research software
\item Open research index
\item Letters of evaluation for computational scientists
\end{enumerate}

>>>>

    \item \textbf{Willem Robert van Hage\textsuperscript{\textasteriskcentered},
    Jason Maassen and Rob van Nieuwpoort: \textit{Software Impact Measurement at the
    Netherlands eScience Center}}~\cite{vanHage:2016ws}.
    This talk described eStep (eScience Technology Platform) at the Netherlands
    eScience Center, which includes three components: a software catalogue
    of eScience software, interfaces, libraries,
    tools workflows, applications, etc.; a knowledge base of guides, reports, and
    recommendations for scientific software development; and eScience research
    documents including such as scientific publications, book chapters, and demos.
    The eStep website currently presents automatically-generated information about
    software based on metadata, with a plan for displaying measures of impact and
    quality.

@@

Once we had the walls covered in ideas, we had people organically form groups around the flip charts on the wall\footnote{Photos of the flipcharts: \url{https://github.com/WSSSPE/media/tree/master/WSSSPE4-photos}}. For those folk who worked on Vision and Gaps, after an hour, we encouraged them to finish their Vision or Gap Google Doc, and to find and join or start working on a project with a group. This led to the 12 groups that are discussed in the rest of this section, specifically:
\begin{enumerate}
\item Verifying best practices \& metrics for sustainable research software
\item Software Sustainability Alliance
\item Scientific Software Prototyping Infrastructure (S2PI)
\item Standard metadata for software (CodeMeta)
\item White paper on developing sustainable software
\item Social science for scientific software
\item Software best practices for undergraduates
\item Meaningful metrics for sustainable software
\item Coordinating access to CI for research software
\item Software engineering processes tailored for research software
\item Open research index
\item Letters of evaluation for computational scientists
\end{enumerate}
